Searching for galaxy assembly bias with the clustering measurements of Sloan Digital Sky Survey

### 2016-05-11 text/ms.tex
text

\title{Constraining galaxy assembly bias with galaxy-galaxy measurements of Sloan Digital Sky Survey}

@@

Throughout this paper, unless stated otherwise, all radii and densities are in comoving units.
Standard flat $\lambda$CDM is assumed, and all cosmological parameters are set to the planck 
2015 best-fit estimates.

@@

The assumption that galaxies reside dark matter halos is the bedrock of the modern cosmology and 
large-scale structure formation theories. One of the most powerfuls model for descibing the galaxy-halo 
connection is the halo occupation modeling. The underlying assumption of the traditional HOD modeling is 
that the halo mass alone is sufficient in determining the population of halos. Despite its simplifying 
assumption, this model has ben widely used in fitting the measurements of galaxy clustering an galaxy-galaxy lensing.

\section{Galaxy-Galaxy Lensing}

In galaxy-galaxy lensing, the connection between dark matter and galaxies is probed by measuring 
the cross correlation between the two. In particular, one can define the galaxy-matter cross correlation 
as the ensemble average of the product of galaxy over densities and matter overdensities
\beq
\xi_{gm}(r) = \langle \delta_{g}(\vec{x}) \delta_{m}(\vec{x}+\vec{r}) \rangle,
\eeq
where $\delta_g$ and $\delta_m$ are overdensities of matter and galaxies respectively and we have 
assumed the cross-corrlation depends only on the radial separation due to isotropy in distribution of matter
and galaxies.

This cross correlation can be related to the azimuthally-averaged  projected surface density of the gravitational
lenses,
\begin{eqnarray}
\Sigma(R) &=& \bar{\rho}_{m}(z)\int_{0}^{\infty} \;  [1 + \xi_{gm}(\sqrt{\chi^2 + R^2})] \; d\chi \nonumber \\
          &=& 2\bar{\rho}_{m}(z)\int_{R}^{\infty} \; [1 + \xi_{gm}(r)] \; \frac{rdr}{\sqrt{r^{2} - R^{2}}}.
\end{eqnarray}

>>>>

\title{Searching for galaxy assembly bias with the clustering measurements of Sloan Digital Sky Survey}

@@

The assumption that galaxies reside dark matter halos is the central tenent of the modern cosmology and 
large-scale structure formation theories. One of the most powerfuls model for descibing the galaxy-halo 
connection is the halo occupation modeling. The underlying assumption of the traditional HOD modeling is 
that the halo mass alone is sufficient in determining the population of galaxies inside halos. 
Despite this simplifying assumption, this model has ben widely---and succesfully---utilized in fitting 
the measurements of galaxy clustering and galaxy-galaxy lensing.

In this investigation, we explore the notion that how the dependence of galaxy-halo connection on 
halo properties beyond mass---such as concentration, age, etc---
Throughout this paper, unless stated otherwise, all radii and densities are in comoving units.
Standard flat $\lambda$CDM is assumed, and all cosmological parameters are set to the planck 
2015 best-fit estimates.

@@

%%%%I'm most likely going to postpone lensing to another manuscript, just wanna focus on clustering
%%%%because I have better handle on that%%%%%%

%\section{Galaxy-Galaxy Lensing}

%In g-g lensing, the connection between dark matter and galaxies is probed by measuring 
%the cross correlation between the two. In particular, one can define the galaxy-matter cross correlation 
%as the ensemble average of the product of galaxy over densities and matter overdensities
%\beq
%\xi_{gm}(r) = \langle \delta_{g}(\vec{x}) \delta_{m}(\vec{x}+\vec{r}) \rangle,
%\eeq
%where $\delta_g$ and $\delta_m$ are overdensities of matter and galaxies respectively and we have 
%assumed the cross-corrlation depends only on the radial separation due to isotropy in distribution of matter
%and galaxies.

%This cross correlation can be related to the azimuthally-averaged  projected surface density of the gravitational
%lenses,
%\begin{eqnarray}
%\Sigma(R) &=& \bar{\rho}_{m}(z)\int_{0}^{\infty} \;  [1 + \xi_{gm}(\sqrt{\chi^2 + R^2})] \; d\chi \nonumber \\
%          &=& 2\bar{\rho}_{m}(z)\int_{R}^{\infty} \; [1 + \xi_{gm}(r)] \; \frac{rdr}{\sqrt{r^{2} - R^{2}}},
%\end{eqnarray}
%where $\chi$ is the projected comoving line-of-sight distance, and $R$ is the projected comoving transverse distance.

%Since the galaxy-matter cross correlation falls off rapidly that in practice thre redshoft evolution of $\xi_{gm}$ 
%can be neglected, integrating only out to a line-fo-sight distance of $\chi=$ 50 Mpc is sufficient. 
%The mean excess projected density $\bar{\Sigma}(R)$ can be approximated by the following radial integral,
%\beq
%\bar{\Sigma}(R , z_{l}) = 2 \rho_{c,0}\Omega_{m,0}\int_{0}^{\mathrm{50Mpc}} \; \xi_{gm}\Big(\sqrt{R^{2}+\chi^{2}},z_{L} \Big)d\chi.
%\eeq
